---
title: "Experiment 1"
author: "Hongmi Lee, Kyungmi Kim, Do-Joon Yi"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: 
      collapse: false
      smooth_scroll: false
    number_sections: true
    theme: cosmo 
    highlight: tango
    code_folding: hide
subtitle: Famous vs. non-famous faces (between-participants design)
mainfont: Noto Sans CJK KR
---

```{r, echo=FALSE}
setwd("~/Dropbox/RProjects/FamSM/")
```

```{css, echo=FALSE}
pre code, pre, code {
  white-space: pre !important;
  overflow-x: scroll !important;
  word-break: keep-all !important;
  word-wrap: initial !important;
}
```

```{r setup, message=FALSE}
set.seed(12345) # for reproducibility
options(knitr.kable.NA = '')

# Some packages need to be loaded. We use `pacman` as a package manager, which takes care of the other packages. 
if (!require("pacman", quietly = TRUE)) install.packages("pacman")
if (!require("Rmisc", quietly = TRUE)) install.packages("Rmisc") # Never load it directly.
pacman::p_load(tidyverse, knitr, car, afex, emmeans, parallel, ordinal,
               ggbeeswarm, RVAideMemoire)
pacman::p_load_gh("thomasp85/patchwork", "RLesur/klippy")

klippy::klippy()
```


# Item Repetition Phase

Twenty four participants were recruited. Half of the participants were exposed to 24 `famous` faces while the other half were exposed to 24 `non-famous` faces (**pre-experimental stimulus familiarity** as a between-participants factor). Each face was repeated eight times, resulting in 192 trials in total. For each face, participants made a male/female judgment. 


```{r, collapse=TRUE}
P1 <- read.csv("data/data_FamSM_Exp1_Face_REP.csv", header = T)
P1$Familiarity = factor(P1$Familiarity, levels=c(1,2), labels=c("Famous","Non-famous"))

glimpse(P1, width=70)
# 1. SID: participant ID
# 2. Familiarity: pre-experimental familiarity. 1 = famous, 2 = non-famous
# 3. RepTime: number of repetitions, 1~8
# 4. Trial: 1~24
# 5. ImgCat: stimulus category. male vs. female
# 6. Resp: male/female judgment, 1 = male, 2 = female, 0 = no response
# 7. Corr: correctness, 1=correct, 0 = incorrect or no response
# 8. RT: reaction times in ms.
# 9. ImgName: name of stimuli

table(P1$Familiarity, P1$SID)
```


## Accuracy

We calculated the mean and *s.d.* of individual participants' mean percentage accuracy. Overall accuracy of the male/female judgment was high. The `famous` condition showed lower mean accuracy and larger variance than the `non-famous` condition. In the following plot, red points and error bars represent the means and 95% CIs.

```{r, fig.height=4}
# phase 1, subject-level, long-format
P1slong <- P1 %>% group_by(SID, Familiarity) %>% 
  summarise(Accuracy = mean(Corr)*100) %>% 
  ungroup()

# summary table
P1slong %>% group_by(Familiarity) %>%
  summarise(M = mean(Accuracy), SD = sd(Accuracy)) %>% 
  ungroup() %>% 
  kable()


# group level, needed for printing & geom_pointrange
# Rmisc must be called indirectly due to incompatibility between plyr and dplyr.
P1g <- Rmisc::summarySE(data = P1slong, measurevar = "Accuracy", groupvars = "Familiarity")

ggplot(P1slong, aes(x=Familiarity, y=Accuracy)) +
  geom_violin(width = 0.5, trim=TRUE) + 
  ggbeeswarm::geom_quasirandom(color = "blue", size = 3, alpha = 0.2, width = 0.2) +
  geom_pointrange(P1g, inherit.aes=FALSE,
                  mapping=aes(x = Familiarity, y=Accuracy, 
                              ymin = Accuracy - ci, ymax = Accuracy + ci), 
                  colour="darkred", size = 1)+
  coord_cartesian(ylim = c(50, 100), clip = "on") +
  labs(x = "Pre-experimental Stimulus Familiarity", 
       y = "Male/Female Judgment \n Accuracy (%)") +
  theme_bw(base_size = 18)
```


### ANOVA

Levene's test indicated that the assumption of homogeneity of variance was not violated. Then, a one-way ANOVA showed that the difference in accuracy was not significant between `famous` vs. `non-famous` conditions.

```{r, warning=FALSE, message=FALSE}
car::leveneTest(Accuracy ~ Familiarity, P1slong)

p1.aov <- aov_ez(id = "SID", dv = "Accuracy", data = P1slong, between = "Familiarity")
anova(p1.aov, es = "pes") %>% kable(digits = 4)
```

<br><br>

****

<br><br>


# Item-Source Association Phase

Participants learned 48 face-location (a quadrant on the screen) associations. They were instructed to pay attention to the location of each face while making a male/female judgment. A between-participants **pre-experimental stimulus familiarity** factor determined whether a participant viewed `famous` or `non-famous` faces. A within-participant **item repetition** factor determined whether a `repeated` item (which had been presented in the first phase) or an `unrepeated` item (which appeared for the first time in the item-source association phase) was presened in each trial.

```{r, collapse=TRUE}
P2 <- read.csv("data/data_FamSM_Exp1_Face_SRC.csv", header = T)
P2$Familiarity = factor(P2$Familiarity, levels=c(1,2), labels=c("Famous","Non-famous"))
P2$Repetition = factor(P2$Repetition, levels=c(1,2), labels=c("Repeated","Unrepeated"))

glimpse(P2, width=70)
# 1. SID: participant ID
# 2. Familiarity: pre-experimental familiarity. 1 = famous, 2 = non-famous
# 3. Trial: 1~48
# 4. Repetition: 1 = repeated, 2 = unrepeated
# 5. ImgCat: stimulus category. male vs. female
# 6. Loc: location (source) of memory item; quadrants, 1~4
# 7. Resp: male/female judgment, 1 = male, 2 = female, 0 = no response
# 8. Corr: correctness, 1 = correct, 0 = incorrect or no response
# 9. RT: reaction times in ms.
# 10. ImgName: name of stimuli

table(P2$Familiarity, P2$SID)
table(P2$Repetition, P2$SID)
```



## Accuracy

We calculated the mean and *s.d.* of individual participants' mean percentage accuracy. Overall accuracy was high. The `non-famous, unrepeated` condition showed slightly lower mean accuracy than the other conditions.

```{r, fig.height=4}
# phase 2, subject-level, long-format
P2slong <- P2 %>% group_by(SID, Familiarity, Repetition) %>% 
  summarise(Accuracy = mean(Corr)*100) %>% 
  ungroup()

# summary table
P2g <- P2slong %>% group_by(Familiarity, Repetition) %>%
  summarise(M = mean(Accuracy), SD = sd(Accuracy)) %>% 
  ungroup()
P2g %>% kable()

# group level, needed for printing & geom_pointrange
# Rmisc must be called indirectly due to incompatibility between plyr and dplyr.
P2g$ci <- Rmisc::summarySEwithin(data = P2slong, measurevar = "Accuracy", idvar = "SID",
                               withinvars = "Repetition", betweenvars = "Familiarity")$ci
P2g$Accuracy <- P2g$M

ggplot(data=P2slong, aes(x=Familiarity, y=Accuracy, fill=Repetition)) +
  geom_violin(width = 0.7, trim=TRUE) +
  ggbeeswarm::geom_quasirandom(dodge.width = 0.7, color = "blue", size = 3, alpha = 0.2, 
                               show.legend = FALSE) +
  # geom_pointrange(data=P2g,
  #                 aes(x = Familiarity, ymin = Accuracy-ci, ymax = Accuracy+ci, color = Repetition),
  #                 position = position_dodge(0.7), color = "darkred", size = 1, show.legend = FALSE) +
  coord_cartesian(ylim = c(50, 100), clip = "on") +
  labs(x = "Pre-experimental Stimulus Familiarity", 
       y = "Male/Female Judgment \n Accuracy (%)", 
       fill="Item Repetition") +
  scale_fill_manual(values=c("#E69F00", "#56B4E9"),
                    labels=c("Repeated", "Unrepeated")) +
  theme_bw(base_size = 18) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) 
```


### ANOVA

Mean percentage accuracy was submitted to a 2x2 mixed design ANOVA with **pre-experimental stimulus familiarity** as a between-participants factor and **item repetition** as a within-participant factor. Both main effects failed to reach significance. The two-way interaction was marginally significant. 

```{r, warning=FALSE, message=FALSE}
p2.aov <- aov_ez(id = "SID", dv = "Accuracy", data = P2slong, 
                 between = "Familiarity", within = "Repetition")
anova(p2.aov, es = "pes") %>% kable(digits = 4)
```


<br><br>

****

<br><br>


# Source Memory Test Phase

In each trial, participants first indicated in which quadrant a given face appeared during the item-source association phase. Participants then rated how confident they were about their memory judgment. There were 48 trials in total. 

```{r, collapse=TRUE}
P3 <- read.csv("data/data_FamSM_Exp1_Face_TST.csv", header = T)
P3$Familiarity = factor(P3$Familiarity, levels=c(1,2), labels=c("Famous","Non-famous"))
P3$Repetition = factor(P3$Repetition, levels=c(1,2), labels=c("Repeated","Unrepeated"))

glimpse(P3, width=70)
# 1. SID: participant ID
# 2. Familiarity: pre-experimental familiarity. 1 = famous, 2 = non-famous
# 3. Trial: 1~48
# 4. Repetition: 1 = repeated, 2 = unrepeated
# 5. AscLoc: location (source) in which the item was presented in Phase 2; quadrants, 1~4
# 6. SrcResp: source response; quadrants, 1~4
# 7. Corr: correctness, 1=correct, 0=incorrect
# 8. RT: reaction times in ms.
# 9. Confident: confidence rating, 1~4
# 10. ImgName: name of stimuli

table(P3$Familiarity, P3$SID)
table(P3$Repetition, P3$SID)
```


## Accuracy

We calculated the mean and *s.d.* of individual participants' mean percentage accuracy. In the following plot, red points and error bars represent the means and 95% within-participants CIs.

```{r, fig.height=4}
# phase 3, subject-level, long-format
P3ACCslong <- P3 %>% group_by(SID, Familiarity, Repetition) %>% 
  summarise(Accuracy = mean(Corr)*100) %>% 
  ungroup()

# summary table
P3ACCg <- P3ACCslong %>% group_by(Familiarity, Repetition) %>%
  summarise(M = mean(Accuracy), SD = sd(Accuracy)) %>% 
  ungroup() 
P3ACCg %>% kable()

# marginal means of famous vs. non-famous conditions.
P3ACCslong %>% group_by(Familiarity) %>% 
  summarise(M = mean(Accuracy), SD = sd(Accuracy)) %>% 
  ungroup() %>% kable()

# marginal means of repeated vs. unrepeated conditions.
P3ACCslong %>% group_by(Repetition) %>% 
  summarise(M = mean(Accuracy), SD = sd(Accuracy)) %>% 
  ungroup() %>% kable()

# wide format, needed for geom_segments.
P3ACCswide <- P3ACCslong %>% spread(key = Repetition, value = Accuracy)

# group level, needed for printing & geom_pointrange
# Rmisc must be called indirectly due to incompatibility between plyr and dplyr.
P3ACCg$ci <- Rmisc::summarySEwithin(data = P3ACCslong, measurevar = "Accuracy", idvar = "SID",
                              withinvars = "Repetition", betweenvars = "Familiarity")$ci
P3ACCg$Accuracy <- P3ACCg$M

ggplot(data=P3ACCslong, aes(x=Familiarity, y=Accuracy, fill=Repetition)) +
  geom_violin(width = 0.5, trim=TRUE) +
  geom_point(position=position_dodge(0.5), color="gray80", size=1.8, show.legend = FALSE) +
  geom_segment(data=filter(P3ACCswide, Familiarity=="Famous"), inherit.aes = FALSE,
               aes(x=1-.12, y=filter(P3ACCswide, Familiarity=="Famous")$Repeated,
                   xend=1+.12, yend=filter(P3ACCswide, Familiarity=="Famous")$Unrepeated),
               color="gray80") +
  geom_segment(data=filter(P3ACCswide, Familiarity=="Non-famous"), inherit.aes = FALSE,
               aes(x=2-.12, y=filter(P3ACCswide, Familiarity=="Non-famous")$Repeated,
                   xend=2+.12, yend=filter(P3ACCswide, Familiarity=="Non-famous")$Unrepeated),
               color="gray80") +
  geom_pointrange(data=P3ACCg,
                  aes(x = Familiarity, ymin = Accuracy-ci, ymax = Accuracy+ci, group = Repetition),
                  position = position_dodge(0.5), color = "darkred", size = 1, show.legend = FALSE) +
  scale_fill_manual(values=c("#E69F00", "#56B4E9"),
                    labels=c("Repeated", "Unrepeated")) +
  labs(x = "Pre-experimental Stimulus Familiarity", 
       y = "Source Memory Accuracy (%)", 
       fill='Item Repetition') +
  coord_cartesian(ylim = c(0, 100), clip = "on") +
  theme_bw(base_size = 18) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) 
```

The effect of **item repetition** was modulated by the **pre-experimental stimulus familiarity** of the items. For `famous` faces, the locations of `unrepeated` items were better remembered (*novelty benefit*). For `non-famous` faces, the locations of `repeated` items were better remembered (*familiarity benefit*). These crossed effects were on top of the general familiarity benefit, in which source memory was more accurate for `famous` faces than for `non-famous` faces. 

### ANOVA

Mean percentage accuracy was submitted to a 2x2 mixed design ANOVA with **pre-experimental stimulus familiarity** as a between-participants factor (`famous` vs. `non-famous`) and **item repetition** as a within-participant factor (`repeated` vs. `unrepeated`).

```{r, warning=FALSE, message=FALSE}
p3.corr.aov <- aov_ez(id = "SID", dv = "Accuracy", data = P3ACCslong, 
                      between = "Familiarity", within = "Repetition")
anova(p3.corr.aov, es = "pes") %>% kable(digits = 4)
```

The main effect of **pre-experimental stimulus familiarity** and the two-way interaction were both significant. Additionally, we performed two separate one-way repeated-measures ANOVAs as post-hoc analyses. The table below shows the effect of item repetition for `famous` faces.

```{r, warning=FALSE, message=FALSE}
ci95 <- P3ACCswide %>% filter(Familiarity=="Famous") %>% 
  mutate(Diff = Unrepeated - Repeated) %>% 
  summarise(lower = mean(Diff) - qt(0.975,df=n()-1)*sd(Diff)/sqrt(n()),
            upper = mean(Diff) + qt(0.975,df=n()-1)*sd(Diff)/sqrt(n()))

p3.corr.aov.r1 <- aov_ez(id = "SID", dv = "Accuracy", within = "Repetition",
                        data = filter(P3ACCslong, Familiarity == "Famous"))
anova(p3.corr.aov.r1, es = "pes") %>% kable(digits = 4)
```

In the **famous** face group, source memory was more accurate for **unrepeated** than **repeated** faces. The 95% CI of difference between the means was [`r round(ci95[1], digits=2)`, `r round(ci95[2], digits=2)`].
The table below shows the effect of item repetition for `non-famous` faces.

```{r, warning=FALSE, message=FALSE}
ci95 <- P3ACCswide %>% filter(Familiarity=="Non-famous") %>% 
  mutate(Diff = Repeated - Unrepeated) %>% 
  summarise(lower = mean(Diff) - qt(0.975,df=n()-1)*sd(Diff)/sqrt(n()),
            upper = mean(Diff) + qt(0.975,df=n()-1)*sd(Diff)/sqrt(n()))

p3.corr.aov.r2 <- aov_ez(id = "SID", dv = "Accuracy", within = "Repetition",
                        data = filter(P3ACCslong, Familiarity == "Non-famous"))
anova(p3.corr.aov.r2, es = "pes") %>% kable(digits = 4)
```

In the **non-famous** face group, source memory was more accurate for **repeated** than **unrepeated** faces. The 95% CI of difference between the means was [`r round(ci95[1], digits=2)`, `r round(ci95[2], digits=2)`].



### GLMM

To supplement conventional ANOVAs, we tested **generalized linear mixed models (GLMM)** on source memory accuracy. This mixed modeling approach with a binomial link function is expected to properly handle binary data such as source memory responses (i.e., correct or not; [Jaeger, 2008](https://www.sciencedirect.com/science/article/pii/S0749596X07001337)). 

We built the full model (`full1`) with two fixed effects (**pre-experimental stimulus familiarity** and **item repetition**) and their interaction. The model also included maximal random effects structure ([Barr, Levy, Scheepers, & Tily, 2013](https://www.sciencedirect.com/science/article/pii/S0749596X12001180)): both by-participant and by-item random intercepts, and by-participant random slopes for **item repetition**. In case the maximal model does not converge successfully, we built another model (`full2`) with the maximal random structure but with the correlations among the random terms removed ([Singmann, 2018](https://cran.r-project.org/web/packages/afex/vignettes/afex_mixed_example.html#lrt-results)). 

To fit the models, we used the `mixed()` of the `afex` package ([Singmann, Bolker, & Westfall, 2017](https://afex.singmann.science/forums/topic/citing-afex)) which was built on the `lmer()` of the `lme4` package ([Bates, Maechler, Bolker, & Walker, 2015](https://www.jstatsoft.org/article/view/v067i01/0)). The `mixed()` assessed the statistical significance of fixed effects by comparing a model with the effect in question against its nested model which lacked the effect in question. *P*-values of the effects were obtained by likelihood ratio tests (LRT).

```{r, eval=FALSE}
(nc <- detectCores())
cl <- makeCluster(rep("localhost", nc))

full1 <- afex::mixed(Corr ~ Familiarity*Repetition + (Repetition|SID) + (1|ImgName), 
               P3, method = "LRT", cl = cl, 
               family=binomial(link="logit"),
               control = glmerControl(optCtrl = list(maxfun = 1e6)))
full2 <- afex::mixed(Corr ~ Familiarity*Repetition + (Repetition||SID) + (1|ImgName),
               P3, method = "LRT", cl = cl, 
               family=binomial(link="logit"),
               control = glmerControl(optCtrl = list(maxfun = 1e6)), expand_re = TRUE)
stopCluster(cl)
```

```{r, echo=FALSE}
load("RData/afex_FamSM_Exp1_Face_Acc.RData")
```

The table below presents the LRT results of the models `full1` and `full2`.

```{r}
full.compare <- cbind(afex::nice(full1), afex::nice(full2)[,-c(1,2)])
colnames(full.compare)[c(3,4,5,6)] <- c("full1 Chisq", "p","full2 Chisq", "p")
full.compare %>% kable()
```

The *p*-values from the two models were highly similar to each other. Post-hoc analysis results are summarized in the table below. The results from the pairwise comparisons were consistent with those from the ANOVA. Item repetition impaired source memory for `famous` faces whereas it improved source memory for `non-famous` faces. 

```{r}
emmeans(full1, pairwise ~ Repetition | Familiarity, type = "response")$contrasts %>% kable()
```


<br><br>


## Confidence

The following table presents the mean and *s.d.* of individual participants' confidence ratings in each condition. The pattern of confidence ratings was qualitatively identical to that of source memory accuracy: we observed the *novelty benefit* for `famous` faces and the *familiarity benefit* for `non-famous` faces. In the following plot, red points and error bars represent the means and 95% within-participants CIs.

```{r, fig.height=4}
P3CFslong <- P3 %>% group_by(SID, Familiarity, Repetition) %>% 
  summarise(Confidence = mean(Confident)) %>% 
  ungroup()

P3CFg <- P3CFslong %>% 
  group_by(Familiarity, Repetition) %>%
  summarise(M = mean(Confidence), SD = sd(Confidence)) %>% 
  ungroup() 
P3CFg %>% kable()

# marginal means of famous vs. non-famous conditions.
P3CFslong %>% group_by(Familiarity) %>% 
  summarise(M = mean(Confidence), SD = sd(Confidence)) %>% 
  ungroup() %>% kable()

# marginal means of repeated vs. unrepeated conditions.
P3CFslong %>% group_by(Repetition) %>% 
  summarise(M = mean(Confidence), SD = sd(Confidence)) %>% 
  ungroup() %>% kable()

# wide format, needed for geom_segments.
P3CFswide <- P3CFslong %>% spread(key = Repetition, value = Confidence)

# group level, needed for printing & geom_pointrange
# Rmisc must be called indirectly due to incompatibility between plyr and dplyr.
P3CFg$ci <- Rmisc::summarySEwithin(data = P3CFslong, measurevar = "Confidence", idvar = "SID",
                                    withinvars = "Repetition", betweenvars = "Familiarity")$ci
P3CFg$Confidence <- P3CFg$M

ggplot(data=P3CFslong, aes(x=Familiarity, y=Confidence, fill=Repetition)) +
  geom_violin(width = 0.5, trim=TRUE) +
  geom_point(position=position_dodge(0.5), color="gray80", size=1.8, show.legend = FALSE) +
  geom_segment(data=filter(P3CFswide, Familiarity=="Famous"), inherit.aes = FALSE,
               aes(x=1-.12, y=filter(P3CFswide, Familiarity=="Famous")$Repeated,
                   xend=1+.12, yend=filter(P3CFswide, Familiarity=="Famous")$Unrepeated),
               color="gray80") +
  geom_segment(data=filter(P3CFswide, Familiarity=="Non-famous"), inherit.aes = FALSE,
               aes(x=2-.12, y=filter(P3CFswide, Familiarity=="Non-famous")$Repeated,
                   xend=2+.12, yend=filter(P3CFswide, Familiarity=="Non-famous")$Unrepeated),
               color="gray80") +
  geom_pointrange(data=P3CFg,
                  aes(x = Familiarity, ymin = Confidence-ci, ymax = Confidence+ci, group = Repetition),
                  position = position_dodge(0.5), color = "darkred", size = 1, show.legend = FALSE) +
  scale_fill_manual(values=c("#E69F00", "#56B4E9"),
                    labels=c("Repeated", "Unrepeated")) +
  labs(x = "Pre-experimental Stimulus Familiarity", 
       y = "Source Memory Confidence", 
       fill='Item Repetition') +
  coord_cartesian(ylim = c(1, 4), clip = "on") +
  theme_bw(base_size = 18) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())
```

### ANOVA

Individuals’ mean confidence ratings were submitted to a 2x2 mixed design ANOVA with **pre-experimental stimulus familiarity** as a between-participants factor and **item repetition** as a within-participants factor.

```{r, warning=FALSE, message=FALSE}
p3.conf.aov <- aov_ez(id = "SID", dv = "Confidence", data = P3CFslong, 
                      between = "Familiarity", within = "Repetition")
anova(p3.conf.aov, es = "pes") %>% kable(digits = 4)
```

The two-way interaction was significant while neither main effects reached significance. Next we performed two additional one-way repeated-measures ANOVAs as post-hoc analyses. The first table below presents the effect of item repetition for `famous` faces, and the second presents the same effect for `non-famous` faces.

```{r, warning=FALSE, message=FALSE}
ci95 <- P3CFswide %>% filter(Familiarity=="Famous") %>%
  mutate(Diff = Unrepeated - Repeated) %>%
  summarise(lower = mean(Diff) - qt(0.975,df=n()-1)*sd(Diff)/sqrt(n()),
            upper = mean(Diff) + qt(0.975,df=n()-1)*sd(Diff)/sqrt(n()))

p3.conf.aov.r1 <- aov_ez(id = "SID", dv = "Confidence", within = "Repetition",
                         data = filter(P3CFslong, Familiarity == "Famous"))
anova(p3.conf.aov.r1, es = "pes") %>% kable(digits = 4)
```

In the `famous` face group, confidence ratings were higher for **unrepeated** than **repeated** faces. The 95% CI of difference between the means was [`r round(ci95[1], digits=2)`, `r round(ci95[2], digits=2)`].


```{r, warning=FALSE, message=FALSE}
ci95 <- P3CFswide %>% filter(Familiarity=="Non-famous") %>%
  mutate(Diff = Repeated - Unrepeated) %>%
  summarise(lower = mean(Diff) - qt(0.975,df=n()-1)*sd(Diff)/sqrt(n()),
            upper = mean(Diff) + qt(0.975,df=n()-1)*sd(Diff)/sqrt(n()))

p3.conf.aov.r2 <- aov_ez(id = "SID", dv = "Confidence", within = "Repetition",
                         data = filter(P3CFslong, Familiarity == "Non-famous"))
anova(p3.conf.aov.r2, es = "pes") %>% kable(digits = 4)
```

In the `non-famous` face group, confidence ratings were higher for **repeated** than **unrepeated** faces. The 95% CI of difference between the means was [`r round(ci95[1], digits=2)`, `r round(ci95[2], digits=2)`].


### CLMM

The responses from a Likert-type scale are ordinal. Especially for the rating items with numerical response formats containing four or fewer categories, it is recommended to use categorical data analysis approaches, rather than treating the responses as continuous data ([Harpe, 2015](https://ac.els-cdn.com/S1877129715200196/1-s2.0-S1877129715200196-main.pdf?_tid=589e7c17-4d55-49e6-a80f-5aef938a1f44&acdnat=1549722329_bb934739b91ee6554cafadb39565dc25)).

Here we employed the **cumulative link mixed modeling (CLMM)** using the `clmm()` of the package `ordinal` ([Christensen, submitted](https://cran.r-project.org/web/packages/ordinal/vignettes/clm_article.pdf)). The specification of the full model was the same as the `mixed()` above. To determine the statistical significance, the LRT compared models with or without the fixed effect of interest.

```{r, eval=FALSE}
P3R <- P3
P3R$Confident = factor(P3R$Confident, ordered = TRUE)
P3R$SID = factor(P3R$SID)

cm.full <- clmm(Confident ~ Familiarity * Repetition + (Repetition|SID) + (1|ImgName), data=P3R)
cm.red1 <- clmm(Confident ~ Familiarity + Repetition + (Repetition|SID) + (1|ImgName), data=P3R)
cm.red2 <- clmm(Confident ~ Repetition + (Repetition|SID) + (1|ImgName), data=P3R)
cm.red3 <- clmm(Confident ~ 1 + (Repetition|SID) + (1|ImgName), data=P3R) 
```

```{r, echo=FALSE}
P3R <- P3
P3R$Confident = factor(P3R$Confident, ordered = TRUE)
P3R$SID = factor(P3R$SID)

load("RData/clmm_FamSM_Exp1_Face_Conf.RData")
```

```{r}
cm.comp <- anova(cm.full, cm.red1, cm.red2, cm.red3)

data.frame(Effect = c("Familiarity", "Repetition", "Familiarity:Repetition"),
           df = 1, Chisq = cm.comp$LR.stat[2:4], p = cm.comp$`Pr(>Chisq)`[2:4]) %>% kable()
```

The LRT revealed a significant two-way interaction. Neither main effects were significant. Next we performed pairwise comparisons as post-hoc analyses. As shown in the following table, the results of the pairwise comparisons were consistent with those from the ANOVA approach. 

```{r}
emmeans(cm.full, pairwise ~ Repetition | Familiarity)$contrasts %>% kable()
```

Below is the plot of estimated marginal means, which were extracted from the fitted CLMM. The estimated distribution of confidence ratings shows the interaction between **item repetition** and **pre-experimental stimulus familiarity**.

```{r, fig.height=4}
temp <- emmeans(cm.full,~Familiarity:Repetition|cut, mode="linear.predictor")
temp <- rating.emmeans(temp)
temp <- temp %>% unite(Condition, c("Familiarity", "Repetition"))

ggplot(data = temp, aes(x = Rating, y = Prob, group = Condition)) +
  geom_line(aes(color = Condition), size = 1.2) +
  geom_point(aes(shape = Condition, color = Condition), size = 4, fill = "white", stroke = 1.2) +
  scale_color_manual(values=c("#E69F00", "#E69F00", "#56B4E9", "#56B4E9")) +
  scale_shape_manual(name="Condition", values=c(21,24,21,24)) +
  labs(y = "Response Probability", x = "Rating") +
  expand_limits(y=0) +
  scale_y_continuous(limits = c(0, 0.4)) +
  scale_x_discrete(labels = c("1" = "1(Guessed)","4"="4(Sure)")) +
  theme_minimal() +
  theme(text = element_text(size=18))
```

```{r, collapse=TRUE}
ww.conf.t.r1 <- t.test(Confidence ~ Repetition, filter(P3CFslong, Familiarity == "Famous"), paired = TRUE)
sort(abs(ww.conf.t.r1$conf.int))[1:2] # 95% CI of difference between means

ww.conf.t.r2 <- t.test(Confidence ~ Repetition, filter(P3CFslong, Familiarity == "Non-famous"), paired = TRUE)
sort(abs(ww.conf.t.r2$conf.int))[1:2] # 95% CI of difference between means
```


<br><br>


## RT

Only RTs in correct trials were analyzed. Before analysis, we first removed RTs either shorter than 200ms or longer than 10s. Then, from the RT distribution of each condition, RTs beyond 3 *s.d.* from the mean were additionally removed. 

```{r, collapse=TRUE}
cP3 <- P3 %>% filter(Corr==1)

sP3 <- cP3 %>% filter(RT > 200 & RT < 10000) %>% 
  group_by(SID) %>% 
  nest() %>% 
  mutate(lbound = map(data, ~mean(.$RT)-3*sd(.$RT)),
         ubound = map(data, ~mean(.$RT)+3*sd(.$RT))) %>% 
  unnest(lbound, ubound) %>% 
  unnest(data) %>% 
  ungroup() %>% 
  mutate(Outlier = (RT < lbound)|(RT > ubound)) %>% 
  filter(Outlier == FALSE) %>% 
  select(SID, Familiarity, Repetition, RT, ImgName)

100 - 100*nrow(sP3)/nrow(cP3)
```

This trimming procedure removed `r round(100 - 100*nrow(sP3)/nrow(cP3), digits = 2)`% of correct RTs.
  
Since the overall source memory accuracy was not high, only small numbers of correct trials were available after trimming. The following table summarizes the numbers of trials submitted to subsequent analyses. No participant had more than 25 trials per condition. In the `non-famous` group, half of the participants had less than 10 valid trials per condition.

```{r}
sP3 %>% group_by(SID, Familiarity, Repetition) %>% 
  summarise(NumTrial = length(RT)) %>% 
  ungroup %>% 
  group_by(Familiarity, Repetition) %>%
  summarise(Avg = mean(NumTrial), 
            Med = median(NumTrial), 
            Min = min(NumTrial), 
            Max = max(NumTrial)) %>% 
  ungroup %>% 
  kable()
```

```{r, fig.height=3}
den1 <- ggplot(cP3, aes(x=RT)) + 
  geom_density() + 
  theme_bw(base_size = 18) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) 
den2 <- ggplot(sP3, aes(x=RT)) + 
  geom_density() + 
  theme_bw(base_size = 18) + 
  labs(x = "Trimmed RT") + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) 
den1 + den2
```

The overall RT distribution was highly skewed even after trimming. Given limited numbers of RTs and its skewed distribution, any results from the current RT analyses should be interpreted with caution and preferably corroborated with other measures.

We calculated the mean and *s.d.* of individual participants’ mean RTs. The overall pattern of RTs across the conditions was consistent with that of source memory accuracy and confidence ratings. In the following plot, red points and error bars represent the means and 95% within-participants CIs.

```{r, fig.height=4}
P3RTslong <- sP3 %>% group_by(SID, Familiarity, Repetition) %>% 
  summarise(RT = mean(RT)) %>% 
  ungroup()

P3RTg <- P3RTslong %>% group_by(Familiarity, Repetition) %>%
  summarise(M = mean(RT), SD = sd(RT)) %>% 
  ungroup()
P3RTg %>% kable()

# wide format, needed for geom_segments.
P3RTswide <- P3RTslong %>% spread(key = Repetition, value = RT)

# group level, needed for printing & geom_pointrange
# Rmisc must be called indirectly due to incompatibility between plyr and dplyr.
P3RTg$ci <- Rmisc::summarySEwithin(data = P3RTslong, measurevar = "RT", idvar = "SID",
                                   withinvars = "Repetition", betweenvars = "Familiarity")$ci
P3RTg$RT <- P3RTg$M

ggplot(data=P3RTslong, aes(x=Familiarity, y=RT, fill=Repetition)) +
  geom_violin(width = 0.5, trim=TRUE) +
  geom_point(position=position_dodge(0.5), color="gray80", size=1.8, show.legend = FALSE) +
  geom_segment(data=filter(P3RTswide, Familiarity=="Famous"), inherit.aes = FALSE,
               aes(x=1-.12, y=filter(P3RTswide, Familiarity=="Famous")$Repeated,
                   xend=1+.12, yend=filter(P3RTswide, Familiarity=="Famous")$Unrepeated),
               color="gray80") +
  geom_segment(data=filter(P3RTswide, Familiarity=="Non-famous"), inherit.aes = FALSE,
               aes(x=2-.12, y=filter(P3RTswide, Familiarity=="Non-famous")$Repeated,
                   xend=2+.12, yend=filter(P3RTswide, Familiarity=="Non-famous")$Unrepeated),
               color="gray80") +
  geom_pointrange(data=P3RTg,
                  aes(x = Familiarity, ymin = RT-ci, ymax = RT+ci, group = Repetition),
                  position = position_dodge(0.5), color = "darkred", size = 1, show.legend = FALSE) +
  scale_fill_manual(values=c("#E69F00", "#56B4E9"),
                    labels=c("Repeated", "Unrepeated")) +
  labs(x = "Pre-experimental Stimulus Familiarity", 
       y = "Response Times (ms)", 
       fill='Item Repetition') +
  theme_bw(base_size = 18) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())
```


### ANOVA

Individuals’ mean RTs were submitted to a 2x2 mixed design ANOVA with **pre-experimental stimulus familiarity** as a between-participants factor and **item repetition** as a within-participant factor.[^1]

```{r, warning=FALSE, message=FALSE}
p3.rt.aov <- aov_ez(id = "SID", dv = "RT", data = sP3, 
                      between = "Familiarity", within = "Repetition")
anova(p3.rt.aov, es = "pes") %>% kable(digits = 4)
```

The two-way interaction was significant. We then performed two one-way repeated-measures ANOVAs as post-hoc analyses. The first table below presents the effect of item repetition for `famous` faces, and the second table presents the same effect for `non-famous` faces.

```{r, warning=FALSE, message=FALSE}
p3.rt.aov.r1 <- aov_ez(id = "SID", dv = "RT", within = "Repetition",
                         data = filter(sP3, Familiarity == "Famous"))
anova(p3.rt.aov.r1, es = "pes") %>% kable(digits = 4)
```

The effect of item repetition was not significant in the `famous` condition.


```{r, warning=FALSE, message=FALSE}
p3.rt.aov.r2 <- aov_ez(id = "SID", dv = "RT", within = "Repetition",
                         data = filter(sP3, Familiarity == "Non-famous"))
anova(p3.rt.aov.r2, es = "pes") %>% kable(digits = 4)
```

The effect of item repetition was not significant in the `non-famous` condition, either.



<br><br>

****

<br><br>


# Session Info
```{r, collapse=TRUE}
sessionInfo()
```

[^1]: 
We additionally tested several GLMMs on source memory RTs since GLMMs with relevant link functions were supposed to be better than the conventional ANOVA in dealing with such limited, unbalanced and skewed data as the current RTs ([Lo & Andrews, 2015](https://p3w.frontiersin.org/articles/10.3389/fpsyg.2015.01171/full)). Some models adopted non-linear transformations of RTs (such as -1000/RT or log(RT)) and  others assumed an inverse Gaussian or Gamma distribution and a linear relationship (identity link function) between the predictors and RTs. None of the models, however, converged onto a stable solution. 